Quantum Interval-Valued Probability: Contextuality and the Born Rule

### 2018-03-25 revised_prop_letter_ajhs.tex
revised_prop_letter_ajhs.tex Fix some typos...

\NewDocumentCommand{\newInterval}{o o o o}{
 \newcommand{#1}{\text{\wesa{{#2}}}}
 % \newcommand{#1}{\ensuremath{\left[{#3}\right]}}
 % \newcommand{#1}{\ensuremath{I\left({#4}\right)}}
}
%% \newInterval[\imposs][impossible][0,0][0]
%% \newInterval[\likely][likely][\tfrac{1}{2},1][\tfrac{1}{2},1]
%% \newInterval[\unlikely][unlikely][0,\tfrac{1}{2}][0,\tfrac{1}{2}]
%% \newInterval[\necess][certain][1,1][1]
%% \newInterval[\unknown][unknown][0,1][0,1]
\newInterval[\midd][middle][\tfrac{1}{4},\tfrac{3}{4}][\tfrac{1}{4},\tfrac{3}{4}]

@@

In this investigation, we explore the implications of extending
conventional quantum-mechanical probability measures to include the
effect of imperfect measurements.  There are long-standing debates in
the foundations of quantum mechanics regarding the tension between
finite precision measurement and
contextuality~\cite{BarrettKent2004,Appleby_2005}. The outcome of a
theory that is contextual depends upon whether compatible sets of
observables are measured together or separately; a non-contextual
theory gives the same results in either case.  A classic example of
the varying opinions on the impact of imprecision is the claim by
Meyer~\cite{PhysRevLett.83.3751} that finite-precision measurements
invalidate the spirit of the Kochen-Specker theorem. This claim was
countered in the same year by Havlicek et al. ~\cite{HKSS1999apsrev4}
and Mermin~\cite{Mermin1999} and the debate continues to be an active
topic of
research~\cite{Kent1999,HavlicekKrennSummhammerSvozil2001,SimonBruknerZeilinger2001,Cabello2002,Larsson2002,Appleby2002,BarrettKent2004,Appleby_2005,Spekkens2005,GuehneKleinmannCabelloEtAl2010,MazurekPuseyKunjwalEtAl2016}.

@@

\begin{thm}[Finite-Precision Extension of the Gleason Theorem]\label{thm:Finite-precision-Gleason-1}Let
$f:\left[0,1\right]\rightarrow\mathscr{I}$ be a blurring function
and let $f\circ\muB_{\rho}$ be a QIVPM, where $\muB_{\rho}$ is the
probability measure induced by the Born rule for a given state~$\rho$.
Let $\alpha$ be the maximum length of intervals in $\mathscr{I}$.
If a state $\rho'$ is consistent with $f\circ\muB_{\rho}$ on all
events, i.e., $\rho'\in\coreBorn\left(f\circ\muB_{\rho},\events\right)$,
then the norm of their difference is bounded by $\alpha$, i.e., $\left\Vert \rho-\rho'\right\Vert \le\alpha$.\end{thm}

>>>>

@@

In this investigation, we explore the implications of extending
conventional quantum-mechanical probability measures to include the
effect of imperfect measurements.  There are long-standing debates in
the foundations of quantum mechanics regarding the tension between
finite precision measurement and
contextuality~\cite{BarrettKent2004,Appleby_2005}. The outcome of a
theory that is contextual depends upon whether compatible sets of
observables are measured together or separately; a non-contextual
theory gives the same results in either case.  A classic example of
the varying opinions on the impact of imprecision is the claim by
Meyer~\cite{PhysRevLett.83.3751} that finite-precision measurements
invalidate the spirit of the Kochen-Specker theorem. This claim was
countered in the same year by Havlicek et al. ~\cite{HKSS1999apsrev4}
and Mermin~\cite{Mermin1999} and the debate continues to be an active
topic of
research~\cite{Kent1999,SimonBruknerZeilinger2001,Cabello2002,Larsson2002,Appleby2002,BarrettKent2004,Appleby_2005,Spekkens2005,GuehneKleinmannCabelloEtAl2010,MazurekPuseyKunjwalEtAl2016}.

@@

\begin{thm}[Finite-Precision Extension of the Gleason Theorem]\label{thm:Finite-precision-Gleason}Let
$f:\left[0,1\right]\rightarrow\mathscr{I}$ be a blurring function
and let $f\circ\muB_{\rho}$ be a QIVPM, where $\muB_{\rho}$ is the
probability measure induced by the Born rule for a given state~$\rho$.
Let $\alpha$ be the maximum length of intervals in $\mathscr{I}$.
If a state $\rho'$ is consistent with $f\circ\muB_{\rho}$ on all
events, i.e., $\rho'\in\coreBorn\left(f\circ\muB_{\rho},\events\right)$,
then the norm of their difference is bounded by $\alpha$, i.e., $\left\Vert \rho-\rho'\right\Vert \le\alpha$.\end{thm}
